---
output:
  md_document:
    variant: markdown_github
---

# Bird Color Palettes (made with 100% REAL birds!)

birdcolors is a palette generator to spice up your scientific plots (and maybe your life) using the diversity of colors observed across the birds of the world.

Cite us: Tonelli, B.A. (2025) birdcolors: A palette generator of bird colors. R package version 0.0.5

## Install

```{r,eval=FALSE}
devtools::install_github("bentonelli/birdcolors")
```

## Basic Use

### See what birds are being recommended today
```{r}
library(birdcolors)
library(ggplot2)

#Get recommended birds - visually appealing and colorblind friendly!
bird_menu("rec")

#For all available birds, use: bird_menu("all")
```
### Visualize these recommended palettes
```{r}
bird_palette_visualizer(all_or_rec = "rec",pdf_plot = FALSE)
```

### Plotting discrete colors with base R
```{r}
# Base R

#Use the bird colors function to load in your favorite bird's colors.
outp <- bird_colors("Scarlet Macaw")


xx <- (1:7)
yy <- (1:7)
zz <- (1:7)

plot(xx,yy,col=outp[zz],pch=19,cex=2)
```

### Plotting with ggplot
```{r}
# ggplot2
bird_cols <- bird_colors("Lovely Sunbird",reverse=TRUE)

xx <- rnorm(1000,0,1)
yy <- rnorm(1000,0,1)
zz <- xx

ggplot() +
  geom_point(aes(x = xx,y=yy,col=zz),pch=19,cex=2) +
  scale_color_bird(bird_cols,midpoint=0) +
  theme_classic()
```
